---
title: |
  | Logic and Functions
  | UC Davis Statistics Club
author: |
  | Created by:
  | Christopher Wong
  | Academic Director
output: 
  beamer_presentation:
    includes:
      in_header: C:/Users/Christopher/Desktop/Statistics Club/watermark.tex
# keep_tex: true
    slide_level: 3
---
```{r set-options, echo = FALSE}
options(width = 50)
```

### Logic

- Mathematical and logical symbols
\begin{itemize}
  \item Less than: \textbf{<}
  \item Greater than: \textbf{>}
  \item Less than or equal to: \textbf{<=}
  \item Greater than or equal to: \textbf{>=}
  \item Equals: \textbf{==}
  \item Addition, subtraction, multiplication, division: \textbf{+, -, *, /}
  \item Modulus: \textbf{\%\%}
  \item And: \textbf{\&} and \textbf{\&\&}
  \item Or: \textbf{$\mid$} and \textbf{$\parallel$}
  \begin{itemize}
    \item $\&$ and $\mid$ performs elementwise comparisons, $\&\&$ and $\parallel$ is more appropriate for control-flow (e.g. loops)
  \end{itemize}
  \item Not: \textbf{!}
\end{itemize}

### Logical statements and Loops

- Logical statements
\begin{itemize}
  \item if(statement)\{code\} evaluates if the statement is TRUE or FALSE. If TRUE, then the code is run.
  \item else\{code\} comes after an if(statement) and the code is run when the if(statement) returns FALSE.
  \item else if(statement)\{code\} adds additional if(statement) to the code if the first if(statment) returns FALSE.
  \item ifelse(statement, TRUE, FALSE) is a compact way of writing an if and else statement.
  \item while(statement)\{code\} continues to run until the statement is FALSE
\end{itemize}

----

- Loops
\begin{itemize}
  \item for(i in 1:length(foo)){} For loops are not recommended as they are slow in R. Instead, we use
  \item sapply(1:length(foo), function()) for vectors and data frames and
  \item lapply(1:length(foo), function()) for lists
  \item aggregate(data, by = list(), FUN = function) applies the function to the data after splitting them into subsets based on factors specified in by = list().
\end{itemize}

### Writing your own functions

- R gives you the ability to write your own functions with **function()**

```{r, eval = FALSE, comment = "#"}
# This is where you will combine your R knowledge
# (subsetting, logical statements, loops, basic functions).
example.func = function(variables){
  Code goes here.
  return (Results)
}
```

---

- Data sampler/subsetter
- Probability and simulation
- Confidence intervals and visualization
- Data destroyer/cleaner
- Outlier finder

### Bonus Topics

- Contrast of simulation and theory
\begin{itemize}
  \item Limits and infinite sums
  \item Fibonacci numbers
\end{itemize}